%-------------------------
% Resume in Latex
% Author : Redacted for Privacy
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks,colorlinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{ulem}
\usepackage{calc}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage{charter}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\censor}[1]{\textcolor{black}{\rule{\widthof{#1}}{1.2ex}}}

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\hypersetup{%
     colorlinks=true,
     linkcolor=blue,
     filecolor=blue,
     citecolor=black,      
     urlcolor=teal,
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------

\begin{center}
	\textbf{\Huge \scshape John Doe} \\ \vspace{1pt}
	\href{mailto:email@example.com}{\underline{email@example.com}} $|$ 
	\href{https://linkedin.com/in/example}{\underline{linkedin.com/in/example}} $|$
	\href{https://github.com/example}{\underline{github.com/example}} \\
	+1 (XXX) XXX-XXXX $|$ City, State
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\censor{HARMAN International India Pvt. Ltd.}}{\censor{Bangalore}}
{Associate Engineer – Embedded C++}{Jul 2024 -- Present}
\resumeItemListStart
\resumeItem{Rescued an escalated \textbf{Tier-1 OEM} project by redesigning \textbf{diagnostic recorder} and extending \textbf{CAN Data Sampler} to meet strict \textbf{real-time data collection} requirements—despite hardware constraints preventing true real-time streaming.}
\resumeItem{Led daily technical discussions with \textbf{OEM engineers} to clarify requirements and iterated solutions, delivering a robust workaround that satisfied the customer and passed \textbf{acceptance testing}.}
\resumeItem{Engineered a hybrid sampling logic to collect \textbf{CAN data} with accurate \textbf{timestamps} and \textbf{validity checks} from filtered \textbf{shared memory}, ensuring \textbf{80+ hour diagnostic data retention} and reliable fault detection.}
\resumeItem{Eliminated \textbf{scheduler drift} in \textbf{CAN/Lua pipeline} that was corrupting long-run OEM scripts, restoring multi-hour data integrity.}
\resumeItem{Reduced \textbf{gRPC} CPU usage from \textbf{30\% to 5\%}, preserving \textbf{TCU} headroom for safety-critical services (e.g., \textbf{E-call}) and avoiding scope reduction.}
\resumeItem{Developed reusable \textbf{HTTP/2 + mTLS} \textbf{C++17} library with \textbf{eSIM-based certificate retrieval}, cutting secure comms development time across projects.}
\resumeItemListEnd

\resumeSubheading
{\censor{HARMAN International India Pvt. Ltd.}}{\censor{Bangalore}}
{Intern – Embedded C++ Developer}{Dec 2023 -- Jun 2024}
\resumeItemListStart
\resumeItem{Designed and implemented core \textbf{CAN Data Sampler} with multiple collection modes (simple, change-point, hybrid) and sub-second shared memory IPC, forming the backbone of production diagnostics.}
\resumeItem{Created \textbf{Lua-based runtime scheduler} enabling configurable data processing without firmware redeploy.}
\resumeItem{Implemented \textbf{gRPC} streaming from shared memory buffers for near-real-time diagnostics with minimal CPU overhead.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Open Source Contributions}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\href{https://github.com/starship/starship}{starship}} – Cross-shell prompt (50k+ stars)}{Aug 2025}
\resumeItemListStart
\resumeItem{Implemented C++ project detection in Rust, merged in v1.23.0 (\href{https://github.com/starship/starship/pull/6570}{PR \#6570}).}
\resumeItem{Fixed Rust 1.89.0 lifetime elision warnings breaking CI builds and resolved test stalls caused by interactive GPG prompts, restoring reliable CI for all contributors (\href{https://github.com/starship/starship/pull/6887}{PR \#6887}).}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/tock/tock}{Tock OS}} – Rust-based embedded OS (5k+ stars)}{Dec 2024}
\resumeItemListStart
\resumeItem{Fixed documentation errors, improving developer onboarding (\href{https://github.com/tock/tock/pulls?q=is\%3Apr+author\%3Asiddharthkumarjha}{PRs}).}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/AdnanHodzic/auto-cpufreq}{auto-cpufreq}} – Linux CPU power manager (6k+ stars)}{May 2023}
\resumeItemListStart
\resumeItem{Fixed Arch Linux auto-start issues and updated documentation (\href{https://github.com/AdnanHodzic/auto-cpufreq/releases/tag/v1.9.8}{v1.9.8}).}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages}{: C, C++17, Lua, Bash, Rust} \\
		\textbf{Tools}{: GDB, CMake, Git, Codesonar, SQLite} \\
		\textbf{Embedded}{: ARMv7l, SHM, IPC, CAN, RTOS concepts, Telux API} \\
		\textbf{Protocols}{: gRPC, HTTP/2, MQTT, mTLS} \\
		\textbf{Libraries}{: libcurl}
	}}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{\censor{Kalinga Institute of Industrial Technology}}{\censor{Bhubaneshwar, Odisha}}
{B.Tech in Computer Science and Engineering}{Jul 2020 -- May 2024}
\resumeSubHeadingListEnd

\end{document}
